Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Added side length to Figure 4

@@

@@

a1 <- tibble(x = all_centroids_df_temp$c_x[4],
             xend = all_centroids_df_temp$c_x[5],
             y = all_centroids_df_temp$c_y[21],
             yend = all_centroids_df_temp$c_y[21],
             label = expression(a[1]))
a2 <- tibble(x = all_centroids_df_temp$c_x[25],
             xend = all_centroids_df_temp$c_x[25],
             y = all_centroids_df_temp$c_y[25],
             yend = all_centroids_df_temp$c_y[33],
             label = expression(a[2]))

@@

>>>>

a1_temp <- hb_obj_notation$a1
a2_temp <- hb_obj_notation$a2
l_temp <- quad(a=3, b = 2 * a2_temp, c = -(a2_temp^2 + a1_temp^2))

@@

hex_grid_temp45 <- hex_grid_temp |> 
  filter(hex_poly_id == 45)

@@

a1 <- tibble(x = all_centroids_df_temp$c_x[4],
             xend = all_centroids_df_temp$c_x[5],
             y = all_centroids_df_temp$c_y[21],
             yend = all_centroids_df_temp$c_y[21],
             label = expression(a[1]))
a2 <- tibble(x = all_centroids_df_temp$c_x[25],
             xend = all_centroids_df_temp$c_x[25],
             y = all_centroids_df_temp$c_y[25],
             yend = all_centroids_df_temp$c_y[33],
             label = expression(a[2]))
l <- tibble(x = hex_grid_temp45$x[2],
            xend = hex_grid_temp45$x[3],
            y = hex_grid_temp45$y[2],
            yend = hex_grid_temp45$y[3],
            label = expression(l))

@@

  geom_segment(data = l, aes(
    annotate("text", x=l$x + 0.03, y=(l$y+l$yend)/2, 
             label = expression(l), 
